---
title       : MyShinyApp Pitch
subtitle    : DDP Project on Coursera
author      : Stephen Sani
job         : Presenter
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## MyShinyApp
The data used by this app is the built-in mtcars data in R

The codes for the app are in two files: ui.R and server.R

The App provides: 
* summaries for two selected variables of the data 
* a histogram for each of the two selected variables 
* a scatter plot for both variables




--- .class #id 
## What the server does

The server loads the mtcars data
```{r}
data("mtcars")
```

the fields for the data are

```{r}
colnames(mtcars)
```

The server provides the summaries for the selected fields along with plots of the individual fields and their interaction.

---
## What the User interface does

The user interface allows the user to select two fields on the mtcars data.
The interface provides for two numeric intput fields that allows for numeric input from 0.
Numeric inputs from 1 t0 11 corresponds to field values.
```{r}
data.frame(numericInput = c(1:11), fieldName = colnames(mtcars))
```

---
## find MyShinyApp @


https://sani3.shinyapps.io/MyShinyApp



